Tidal field anisotropy as a tracer of cosmic voids

### 2014-12-20 cosmic_voids.tex
introduccion revisada

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as a tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

%%

The tidal and the shear tensors have proven to be more fundamental than 
the density field as they also trace the collapsing or expanding nature of 
the matter field, which ultimately is what defines the underlying dynamics 
of the Cosmic Web. Furthermore, the density field is degenerated regarding 
the defined types of environment \citep{Hahn07}, which implies that is not 
possible to assign a priori a range of density values to each of them. 
This yields that the usually adopted definition of voids as simply 
underdense regions in the large-scale matter distribution, is not precise 
enough as it excludes a proper description of the internal structure of 
voids.

Following the recent trend of using digital image-processing techniques 
developed in other disciplines (e.g. medical sciences and computer imaging) 
for analysing the structure of the Cosmic Web, we propose here, much in 
the same way as \citet{Libeskind13}, the fractional anisotropy (FA) as a 
tracer of the internal structure and the outline of cosmic voids. The FA 
was initially introduced by \citet{Basser95} for quantifying the 
anisotropy degree of the diffusivity of water molecules through cerebral
tissue in nuclear magnetic resonance imaging. In this context we use the 
same quantity for determining the anisotropy degree of the local 
environment from either the orbital dynamics as set by the eigenvalues of
the tidal tensor (Tweb), or the dynamics of the velocity field as set by 
the eigenvalues of the shear tensor (Vweb). In both cases, the FA is not
determined directly from the density field, it hence is suitable for 
describing both, the structure of high non-linear regions (e.g. filaments,
knots and very dense walls) as well as the fainter substructure exhibited 
by quasi-linear regions like voids.

Once established the FA as the tracer field of cosmic voids, we proceed to
identify individual voids as basins of local minima. For this purpose we
implement a technique developed by \citet{Beucher79} and \citet{Beucher93} 
and widely used in the field of image analysis and mathematical morphology, 
i.e. the \textit{watershed transform algorithm}. This technique has been 
already implemented on void finding schemes by \citet{Platen07} and 
\citet{Neyrinck08} with very interesting results, where individual voids 
are identified as catching basins of local minima of the density field. 
The appeal of this algorithm consists in that is parameter-free and does 
not require any assumption on the shape and morphology of voids. 
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

This paper is organized as follows. In section 2 we describe the used
simulation for testing our void finding algorithm, i.e. the Bolshoi
simulation. A detailed description of these methods is presented in 
section 3. In section 4 we describe how the FA can be used for tracing the 
structure of voids. Once obtained meaningful catalogues of voids for each 
scheme, we proceed to compare some typical and general interest properties 
of voids such as volume functions, distributions of size and density and 
velocity profiles. This is done in section 5. Finally in section 6 we 
analyse and evaluate our findings.

%*************************************************************************
\section{The Simulation}
\label{sec:the_simulation}
%*************************************************************************

@@

%*************************************************************************
\section{Finding voids}
\label{sec:bulk_voids}
%*************************************************************************

@@

@@

%*************************************************************************
\section{Properties of voids}
\label{sec:properties}
%*************************************************************************

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Tidal field anisotropy as a tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

This procedure allows a new description of the internal structure
of voids that goes beyond a simple definition of a void as just an
underdense regions in the large-scale matter distribution.
The tidal and the shear tensors encode more information than the
density field as they trace the collapsing or expanding
nature of the matter field, which defines the dynamics of the Cosmic
Web.

The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA  was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance
imaging.
\citet{Libeskind13} introduced this concept in the context of Cosmic
Web classification schemes.

Once we establish the FA as a conveniente tracer for voids, we proceed to
identify individual voids as basins of local minima. For this purpose we
implement a \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} which has been already implemented on void
finding schemes\citep{Platen07,Neyrinck08} defining voids as catching
basins of local minima of the density field.  
We use insted minima of the FA field to find define the voids.

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
Then in Section \ref{sec:bulk_voids} we explain in detail our void
finder based on the fractional anisotropy of the tidal and shear
tensor fields. 
In Section \ref{sec:experiments} we describe the setup
for the numerical experiments we perform to show the performance of
the new void finding technique. 
Our results are presented in \ref{sec:results} to finally comment and
conclude about this findings in Section \ref{sec:conclusions}.

@@

%*************************************************************************
\section{A new void finding technique}
\label{sec:bulk_voids}
%*************************************************************************

@@

\subsection{Watershed algorithm}
\label{sec:watershed}

This algorithm is parameter-free and does  not require any assumption
on the shape and morphology of voids.  
Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
Cartesian mesh for estimating the density and tensor fields, instead of 
the more sophisticated \textit{Delaunay tessellation for field estimator} 
(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
watershed transform should not be significantly affected as we are 
interested in low density regions where the \texttt{CIC} gives similar 
estimations.

@@

%*************************************************************************
\section{Numerical Experiments}
\label{sec:experiments}
%*************************************************************************

%*************************************************************************
\section{Results}
\label{sec:results}
%*************************************************************************
